### 2015-11-05 ch02-qlogms/logMS_IMTC.tex
Clean up experiment design a bit

\subsection{Multisine Excitations}
  To excite the system under test we will use multisine excitations \citep{Pintelon2001} with $F$ frequency components:
  \begin{equation}
    u \left( t\right) = \frac{1}{\sqrt{F}}
   \sum_{k=1}^{F} 
     A_k 
     \sin 
       \left(2\pi f_k t + \phi_k \right)
  \text{.}
  \label{eq:MultisineCT}
  \end{equation}
  In this expression, $f_k$ represents the $k^{\text{th}}$ excited frequency component.
  $A_k$ is the amplitude and $\phi_k$ the phase of the $k^{\text{th}}$ spectral line.
  We limit ourselves, without loss of generality, to random phase multisines.
  Hence, $\phi_k$ is the outcome of a uniform random process over $\left[0,2\pi\right[$.
  This leaves two sets of free parameters to create a signal that suits our needs:
    the amplitude of the spectral lines $A_k$ and
    the frequency grid $\left\{f_1, \ldots, f_F \right\}$.
  For simplicity, we will assume this grid is sorted, i.e. $f_1 < f_2 < \ldots < f_F$.
  Note that the $k^{\text{th}}$ term in \eqref{eq:MultisineCT} is has a period $T_k \isdef f_k^{-1}$.

  Consequently, the complete multisine has a period of
  \begin{equation}
    T_{u(t)}  = \lcm \set{T_1, \ldots, T_F}
      = \lcm \set{f_1^{-1}, \ldots, f_F^{-1}}
    \text{,}
  \end{equation}
  where the least common (integer) multiple of the real values $T_k$ is defined as
  \begin{equation}
    \lcm \set{T_1, \ldots, T_F} \isdef
      \min \set{T \given{\forall i \in \set{1,\ldots,F}, \exists n_i \in \NaturalNumbers: n_i T_i = T }}
      \text{.}
   \end{equation}
  Note that this minimum doesn't always exist (e.g. when $f_1 = 1 \unit{Hz}$ and $f_F = \pi \unit{Hz}$), in such cases the multisine is aperiodic.

@@

\subsection{Quasi-Logarithmic Grid Multisine}
  Since most measurement equipment and analysis methods rely on signals with an equidistant frequency grid, we will create a frequency grid
  $\set{f_1, f_2, f_3,\ldots, f_F}$ for which \eqref{eq:logGrid} is approximately 
  valid but with the strict constraint that the frequencies must be a subset 
  of an equidistant frequency grid. This yields the following relation for 
  subsequent frequency lines:
  \begin{equation}
    f_k \approx \alpha \cdot f_{k-1}
    \emspace \forall k \in \set{1,\ldots,F}
  \label{eq:qlogGrid}
  \end{equation}
  under the constraint that
  \begin{equation}
    f_k = N \cdot \Delta f,\; N \in \NN
    \text{.}
    \label{eq:constraintLinGrid}
  \end{equation}
  Such a grid is called a quasi-logarithmic (quasi-log) grid \citep{Pintelon2001}.

@@

\TODO{zin loopt niet goed}
  The covariance matrix $\C_{G\left(\omega_{\interest}\right)}$ of the parametric transfer function, which is pretty hard because the common lack of intuition about this model given the parameters, can be shown \citep{Pintelon2001, Gallager2008, matrixcookbook} to be approximately equal to
  \begin{align}
    \C_{G\left( \omega_{\interest}\right) } \approx
      \InnerQuadraticForm[\HT]
                         {\jac{\interest}}
                         {\FisherInformation_{\theta}^{-1}}
     \label{eq:varPeak}
  \end{align}
  with 
  \begin{equation}
    \FisherInformation_{\theta} =
    2
    \real{
          \InnerQuadraticForm[\HT]
                              {\jac{\excited}}
                              {\C_{X}^{-1}}
          }
    \label{eq:FisherInfo}
  \end{equation}
  the Fisher information matrix \citep{Pintelon2001}.

@@

  Finally, $\C_{X}$ denotes the covariance matrix of $X\left(\omega\right) = G\left(\omega, \theta_0 \right) - \frac{Y_0\left(\omega \right) + E\left( \omega \right)  }{ U\left( \omega \right) } $, evaluated at the excited frequencies $\omega_{\excited}$.
  By assuming that the $X\left( \omega \right) $ are independently distributed over the frequency $\omega$, the variance-covariance matrix $\C_{X}$ is a diagonal matrix \citep{Pintelon2001}:
  \begin{equation}
    \C_{X} =
               \left[ \left.
               \begin{matrix}
                 \frac{\sigma^2_E\left(\omega_1 \right) }
                      {\abs{ U\left(\omega_1 \right)}^2 } & 0 & 0 \\
                 0 & \ddots & 0 \\
                 0 & 0 & \frac{\sigma^2_E\left(\omega_F \right) }
                              {\abs{U\left(\omega_F \right)}^2 }
               \end{matrix}
               \right.^{\vphantom{x}}\right]
    \text{.}
  \end{equation}

>>>>

\subsection{Multisine Excitations}
  To excite the system under test we consider a generalization of multisine excitations \citep{Pintelon2012}:
  \begin{definition}[Generalized multisine] \label{def:generalized-MS}
  A generalized multisine $u(t)$ is a signal consisting of $F$ sine waves with a different frequencies $f_k$, amplitudes $A_k$ and phase shifts $\phi_k$:
  \begin{equation}
    u \left( t\right) = \frac{1}{\sqrt{F}}
   \sum_{k=1}^{F} 
     A_k 
     \sin 
       \left(2\pi f_k t + \phi_k \right)
  \text{.}
  \label{eq:MultisineCT}
  \end{equation}
  For simplicity, one can stipulate that the frequency grid is sorted, i.e. $f_1 < f_2 < \ldots < f_F$.
  \end{definition}

  We limit ourselves, without loss of generality, to random phase multisines.
  Hence, $\phi_k$ is the outcome of a uniform random process over $\left[0,2\pi\right[$.
  This leaves two sets of free parameters to create a signal that suits our needs:
    the amplitude of the spectral lines $A_k$ and
    the frequency grid $\left\{f_1, \ldots, f_F \right\}$.
  Note that the $k^{\text{th}}$ term in \eqref{eq:MultisineCT} is has a period $T_k \isdef f_k^{-1}$.

  Consequently, the complete multisine has a period of
  \begin{equation}
    T_{u(t)}  = \lcm \set{T_1, \ldots, T_F}
      = \lcm \set{f_1^{-1}, \ldots, f_F^{-1}}
    \text{.}
  \end{equation}
  \begin{definition}[Least common (integer) multiple] \label{def:lcm-real}
  The least common multiple of the set of values $T_k \in \RealNumbers$ for $k \in \set{1, \ldots, F}$ is  
  \begin{equation}
    \lcm \set{T_1, \ldots, T_F} \isdef
      \min \set{T \given{\forall k \in \set{1,\ldots,F}, \exists n_k \in \NaturalNumbers: n_k T_k = T }}
   \end{equation}
   if such a minimum exists.
   \end{definition}
  \begin{example}
   Consider a generalized multisine where $f_1 = 1 \unit{Hz}$ and $f_2 = \tfrac{2}{3} \unit{Hz}$.
   The corresponding periods are $T_1 = f_1^{-1} = 1 \unit{s}$ and $T_2 = f_2^{-1} = 1.5 \unit{s}$.
   The overall period of the multisine is $T = n_1 T_1 = n_2 T_2 = 3 \unit{s}$, i.e. $n_1 = 3$ and $n_2=2$.
  \end{example}

  \begin{example}
   Consider the generalized multisine of the previous example to which a spectral component is added at $f_3 = \pi \unit{Hz}$, or equivalently one with a period of $T_3 = \pi^{-1} \unit{s}$.
   Then it is not possible to determine integer values $n_1$, $n_2$, $n_3$ such that $n_1 T_1 = n_2 T_2 = n_3 T_3$.
   Consequently, such a `multisine' is not periodic.
  \end{example}

  This last example illustrates that a least common multiple of real numbers does not always exist.
  Consequently, the generalized multisine of \defref{def:generalized-MS} is not guaranteed to be periodic.

@@

\subsection{Quasi-Logarithmic Grid Multisine}
  Since most measurement equipment and analysis methods rely on signals with an equidistant frequency grid, we will create a frequency grid
  $\set{f_1, f_2, f_3,\ldots, f_F}$ for which \eqref{eq:logGrid} is approximately 
  valid but with the strict constraint that the frequencies must be a subset 
  of an equidistant frequency grid. This yields the following relation for 
  subsequent frequency lines:
  \begin{equation}
    f_k \approx \alpha \cdot f_{k-1}
    \emspace \forall k \in \set{1,\ldots,F}
  \label{eq:qlogGrid}
  \end{equation}
  under the constraint that
  \begin{equation}
    f_k = N \cdot \Delta f,\; N \in \NN
    \text{.}
    \label{eq:constraintLinGrid}
  \end{equation}
  Such a grid is called a quasi-logarithmic (quasi-log) grid \citep{Pintelon2012}.

@@

\TODO{zin loopt niet goed}
  The covariance matrix $\C_{G\left(\omega_{\interest}\right)}$ of the parametric transfer function, which is pretty hard because the common lack of intuition about this model given the parameters, can be shown \citep{Pintelon2012, Gallager2008, matrixcookbook} to be approximately equal to
  \begin{align}
    \C_{G\left( \omega_{\interest}\right) } \approx
      \InnerQuadraticForm[\HT]
                         {\jac{\interest}}
                         {\FisherInformation_{\theta}^{-1}}
     \label{eq:varPeak}
  \end{align}
  with 
  \begin{equation}
    \FisherInformation_{\theta} =
    2
    \real{
          \InnerQuadraticForm[\HT]
                              {\jac{\excited}}
                              {\C_{X}^{-1}}
          }
    \label{eq:FisherInfo}
  \end{equation}
  the Fisher information matrix \citep{Pintelon2012}.

@@

  Finally, $\C_{X}$ denotes the covariance matrix of $X\left(\omega\right) = G\left(\omega, \theta_0 \right) - \frac{Y_0\left(\omega \right) + E\left( \omega \right)  }{ U\left( \omega \right) } $, evaluated at the excited frequencies $\omega_{\excited}$.
  By assuming that the $X\left( \omega \right) $ are independently distributed over the frequency $\omega$, the variance-covariance matrix $\C_{X}$ is a diagonal matrix \citep{Pintelon2012}:
  \begin{equation}
    \C_{X} =
               \left[ \left.
               \begin{matrix}
                 \frac{\sigma^2_E\left(\omega_1 \right) }
                      {\abs{ U\left(\omega_1 \right)}^2 } & 0 & 0 \\
                 0 & \ddots & 0 \\
                 0 & 0 & \frac{\sigma^2_E\left(\omega_F \right) }
                              {\abs{U\left(\omega_F \right)}^2 }
               \end{matrix}
               \right.^{\vphantom{x}}\right]
    \text{.}
  \end{equation}

### 2015-11-05 config/glossaries.inc.tex
Clean up experiment design a bit

\renewcommand{\newacronym}[4][]{\newglossaryentry{#2}{type=\acronymtype,
name={#3},
description={#4},
text={#3},
first={#3\protect\footnote{#3: #4}},
plural={#3\glspluralsuffix},
firstplural={#3\glspluralsuffix\protect\footnote{#3: #4}},
#1}}

@@

\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{SISO}{SISO}{Single Input Single Output}
\newacronym{MIMO}{MIMO}{Multiple Input Multiple Output}
\newacronym{SIMO}{SIMO}{Single Input Multiple Output}
\newacronym{MISO}{MISO}{Multiple Input Single Output}
\newacronym{BLA}{BLA}{Best Linear Approximation}
\newacronym{DUT}{DUT}{Device Under Test}

\newacronym{FRF}{FRF}{frequency response function}
\newacronym{LTI}{LTI}{Linear time-invariant}
\newacronym{ETFE}{ETFE}{Empirical Transfer Function Estimate}

>>>>

\renewcommand{\newacronym}[4][]{\newglossaryentry{#2}{type=\acronymtype,
name={#3},
description={#4},
text={#3},
first={#4~(#3)},
plural={#3\glspluralsuffix},
firstplural={#4~(#3\glspluralsuffix)},
#1}}

@@

\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{SISO}{SISO}{single-input single-output}
\newacronym{MIMO}{MIMO}{multiple-input Multiple Output}
\newacronym{SIMO}{SIMO}{Single Input Multiple Output}
\newacronym{MISO}{MISO}{Multiple Input Single Output}
\newacronym{BLA}{BLA}{best linear approximation}
\newacronym{DUT}{DUT}{device under test}

\newacronym{FRF}{FRF}{frequency response function}
\newacronym{LTI}{LTI}{linear time-invariant}
\newacronym{ETFE}{ETFE}{empirical transfer function estimate}
